The data for this lab came from a HPGe detector collected by Dr. Ross Barnowski. The sources used to generate the spectrum are shown in Table \ref{tab:sources}.

\begin{table}[H]
\centering
\caption{Sources for Lab0}
\label{tab:sources}
\begin{tabular}{@{}lllll@{}}
\toprule
$^{241}$Am & $^{133}$Ba & $^{60}$Co & $^{137}$Cs & $^{152}$Eu \\ \bottomrule
\end{tabular}
\end{table}

The energy calibration was performed using a two-point linear fit between $^{137}$Cs and $^{241}$Am. To perform the calibration, a simple python peak detection script searched the raw spectrum data of $^{137}$Cs and $^{241}$Am looking for the channel containing largest number of counts (photopeak) within the spectrum. The program iterated over the spectrum by channel trying to identify a large delta (40000) in the counts. Because $^{137}$Cs and $^{241}$Am have single gamma ray photopeaks, a large delta ensures no other noise in the signal could be misconstrued as photopeaks.

Once the $^{137}$Cs and $^{241}$Am peaks were discovered, the python function polyfit was used to plot a linear line. The inputs to polyfit were the channel of the peak and the actual gamma-ray photopeak energy as listed in the IAEA Isotope Browser. The polyfit output was a slope and intercept that can be used to translate channel to energy. Next, the peak detection script was used to find the multiple photopeaks in the $^{133}$Ba sprectrum. Lastly, the polyfit "calibration" was applied to the $^{133}$Ba photopeaks and spectrum to calculate approximation error and display the full $^{133}$Ba spectrum.
